---
title: Embedding R code
description: |
  <br>This session will cover embedding R code in qmd.
title-block-banner: true
---

## Session Details

- **Date:** [Day of week], [Month] [Day], [Year]  
- **Time:** [Start time]–[End time] ([morning/afternoon/evening] session)  
- **Location:** [Venue or virtual platform]  
- **Instructor:** [Instructor Name]  

---

# Embedding R code into the website

The quarto markdown `.qmd` is essentially a successor to RMarkdown,
mostly backward compatible and following similar syntax.

## Code chunks

```{r}
#| warning: false
#| code-fold: false

library(ape)
library(phangorn)

tree1 <- ape::read.tree(text='(((A,B),C),D);')
tree2 <- ape::read.tree(text='(((A,C),B),D);')

dist <- phangorn::RF.dist(tree1, tree2)

dist
```

## Library loading

Here we are loading the libraries used throughout this document.

```{r}
#| code-fold: false

library(ape)
library(phangorn)
```

## Cross reference figures

You can add special tags to be able to create links to figures.
See @fig-linkable for details.

```{r}
#| label: fig-linkable
#| fig-cap: "You can link to this figure"
#| warning: false
#| code-fold: true

tree1 <- ape::read.tree(text='(((A,B),C),D);')

plot(tree1)
```

## Reading external datasets

We can also read in files that are provided in a relative location to this document.

```{r}

my.trees <- ape::read.nexus('../data/example.trees')

phangorn::RF.dist(my.trees)

```

